Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2012-08-02 paper/paper.tex
added ack

\begin{figure*}[tb]
    \centering
    \subfloat[Ratio of Simulated Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-cost-all}
    }
    \hspace{2cm}
    \subfloat[Ratio of Simulated Makespan to Deadline]{
        \includegraphics[width=0.4\textwidth]{run-finish-variations-test-0-output-makespan-all}
    }
    \caption{Boxplots for budget and deadline ratios when runtime estimate 
    error varies from $\pm$0\% to $\pm$50\% for all three algorithms. Values 
    greater than 1 indicate that the budget/deadline constraint was exceeded.}
    \label{fig:variances}
\end{figure*}

@@

\begin{figure*}[tb]
    \centering
    \subfloat[Ratio of Simulated Ensemble Cost to Budget]{
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-cost-montage}
    }
    \hspace{2cm}
    \subfloat[Ratio of Simulated Ensemble Makespan to Deadline]{    
        \includegraphics[width=0.4\textwidth]{run-finish-delays-test-0-output-dagfinish-montage}
    }
    \caption{Boxplots for budget and deadline ratios when provisioning delay 
    varies from 0 seconds to 15 minutes for all three algorithms. Values 
    greater than 1 indicate that the budget/deadline constraint was exceeded.}
    \label{fig:delays}
\end{figure*}

@@

\section*{Acknowledgments}
This work was sponsored by the National Science Foundation under award 
OCI-0943725 (STCI).

>>>>

\begin{figure*}[tb]
    \centering
    \subfloat[Ratio of Simulated Cost to Budget]{
        \includegraphics[width=0.38\textwidth]{run-finish-variations-test-0-output-cost-all}
        }
    \hspace{2cm}
    \subfloat[Ratio of Simulated Makespan to Deadline]{
        \includegraphics[width=0.38\textwidth]{run-finish-variations-test-0-output-makespan-all}
        }
    \caption{Boxplots for budget and deadline ratios when runtime estimate 
    error varies from $\pm$0\% to $\pm$50\% for all three algorithms. Values 
    greater than 1 indicate that the budget/deadline constraint was exceeded.}
    \label{fig:variances}
\end{figure*}

@@

\begin{figure*}[tb]
    \centering
    \subfloat[Ratio of Simulated Ensemble Cost to Budget]{
        \includegraphics[width=0.38\textwidth]{run-finish-delays-test-0-output-cost-montage}
        }
    \hspace{2cm}
    \subfloat[Ratio of Simulated Ensemble Makespan to Deadline]{    
        \includegraphics[width=0.38\textwidth]{run-finish-delays-test-0-output-dagfinish-montage}
        }
    \caption{Boxplots for budget and deadline ratios when provisioning delay 
    varies from 0 seconds to 15 minutes for all three algorithms. Values 
    greater than 1 indicate that the budget/deadline constraint was exceeded.}
    \label{fig:delays}
\end{figure*}

@@

\section*{Acknowledgments}
This work was supported by the NSF under award OCI-0943725 (STCI) and
by the EU FP7 projects UrbanFlood (248767) and VPH-Share (269978).
